Visualizing the Geography of Genetic Variants

### 2016-06-30 paper.Rmd
adding figures

```{r figure1, echo=FALSE, message=FALSE, fig.height=5, fig.width=5, fig.align='center', fig.cap='Figure caption'}
img <- readPNG("figures/figure1.png")
grid.raster(img)
```

@@

@@

@@

@@

>>>>

```{r figure1, echo=FALSE, message=FALSE, fig.height=5, fig.width=5, fig.align='center', fig.cap='Figure caption'}
img <- readPNG("figures/png/figure1.png")
grid.raster(img)
```

@@

```{r figure2, echo=FALSE, message=FALSE, fig.height=5, fig.width=5, fig.align='center', fig.cap='Figure caption'}
img <- readPNG("figures/png/figure2.png")
grid.raster(img)
```

@@

```{r figure3, echo=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align='center', fig.cap='Figure caption'}
img <- readPNG("figures/png/figure3.png")
grid.raster(img)
```

@@

```{r figure4, echo=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align='center', fig.cap='Figure caption'}
img <- readPNG("figures/png/figure4.png")
grid.raster(img)
```

@@

```{r figure5, echo=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align='center', fig.cap='Figure caption'}
img <- readPNG("figures/png/figure5.png")
grid.raster(img)
```
